---
title: "Pomodoro_Vignette"
author: "Seyma Kalay"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pomodoro_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pomodoro)
```

This package was set for the Credit Access studies. But it can be used for the binary and multiple factor variables. 
First thing let's see the str of the *sample_data* with `str(sample_data)`. Since the dataset is huge, let's take the first 500 rows and set the study on it.

The following example run the `multinominal logistic model` in `yvar`. The function simplifies the 80/20 train test set using 10cv after scaled and center it.

```{r MLR, echo=FALSE}
sample_data <- sample_data[1:500,]
yvar  <- c("Loan.Type")
m2.xvar0 <- c("sex", "married", "age", "havejob", "educ", "rural", "region","income","political.afl") 
#m2.xvar1 <- c(m2.xvar0, "networth")   # with "networth"
BchMk.MLR.1 <- Multinomial_Logit_Model(sample_data, c(m2.xvar0,"networth"), yvar)
BchMk.MLR.1
BchMk.MLR.1$finalModel
BchMk.MLR.1$Roc$auc
```


### Estimate_Models

Estimate_Models function considers `exog` and `xadd` variables and set multiple models based on the selected `exog` and `xadd`.
On the one hand `exog` is subtract the selected vector from the dataset and run the model for all the dataset and for the splits of the `exog`.
On the other hand `xadd` add the selected vectors and run the model.
Where the `dnames` are the unique values in `exog` this is to save the model estimates by their name.

```{r EstModel, echo=FALSE}
sample_data <- sample_data[1:500,]
library(dplyr)
CCP <- sample_data %>% filter(sample_data$political.afl==1)
NoCCP <- sample_data %>% filter(sample_data$political.afl==0)

yvar  <- c("Loan.Type")
m2.xvar0 <- c("sex", "married", "age", "havejob", "educ", "rural", "region","income","political.afl") #, "ethnicity" "class.of.HH",


# CCP.MLR.1 <-  RF_Model(CCP, m2.xvar1, yvar)
# NoCCP.MLR.1 <-  RF_Model(NoCCP, m2.xvar1, yvar)

CCP.RF.1  <- Estimate_Models(sample_data, yvar=c("Loan.Type"), exog = "political.afl", xvec=m2.xvar0, xadd="networth", type="RF", dnames=c("0","1"))
CCP.RF.1
```

### Combined_Performance

Estimate_Models gives the results based on the splits of the `exog`. 
Combined_Performance prints out the total performance of these splits.

```{r ComPerf, echo=FALSE}
CCP.MLR.1 <-  RF_Model(CCP, m2.xvar0, yvar)
NoCCP.MLR.1 <-  RF_Model(NoCCP, m2.xvar0, yvar)

Sub.CCP.MLR.RF <- list(Mdl.1 = CCP.MLR.1,  Mdl.2 = NoCCP.MLR.1)

# CCP.NoCCP.MLR.1 <- Combined_Performance(CCP.MLR.1, NoCCP.MLR.1)
CCP.NoCCP.MLR.1 <- Combined_Performance(Sub.CCP.MLR.RF)
CCP.NoCCP.MLR.1$Roc$auc
```

